Pilot data analysis

### 2020-11-30 pilot_data_analysis.Rmd
add analysis files, set counterbalancing condition to 3

@@

@@

accuracy_by_participant <- csv_data %>% group_by(source) %>% summarise(acc = mean(corr == 1), N = n())

@@

@@

write_csv(data_to_include, path = "current_data.csv")

@@

@@

>>>>

# explore counterbalancing condition
counterbalancing <- fs::dir_ls(path = "./data", glob = "*.csv") %>%
  map_dfr(read_csv, .id = "source", n_max = 1, col_type = cols(
  .default = col_character(), rt = col_double(), corr = col_integer(), TrialID = col_integer()))

@@

csv_data$device <- ifelse(csv_data$OS %in% c("Linux armv7l", "Linux armv8l"), "android", "computer")

@@

accuracy_by_participant <- csv_data %>% group_by(source) %>% summarise(acc = mean(corr == 1), N = n()) %>% left_join(counterbalancing, by = "source")

@@

participants_to_exclude <- accuracy_by_participant %>% filter(N != 480 | acc <= .8)

@@

write_csv(data_to_include, file = "current_data.csv")

@@

Experimental plot by device

```{r plot_by_device}
plot_raincloud(data_to_include %>% filter(corr == 1 & rt < 1500), x_column = "Condition", y_column = "rt", x_label = "Condition", y_label = "RT in ms (correct responses)", main_title = "RT by condition and word type") + 
  # put labels on the mean for easier comparison
  stat_summary(fun.data = function(x) {data.frame(label = format(mean(x), digits = 2), y = mean(x))}, 
                                      geom = "text",
                                      #width = 1,
                                      position = position_nudge(x = 0.5, y = 0),
                                      #size = 0.2,
                                      color = "black") +
  facet_grid(cols = vars(PrimeDuration), rows = vars(StimulusType, device), labeller = label_context)

@@

```
```{r experiment1_and_2_comparison}
exp1 <- read_csv("Exp 1 data.csv")
